Validate model

### 2024-06-20 Code/06_CreateTablesandPlots_save.Rmd
Final edits

    png(file=paste0("Z:/Project Melanoom/PaperMelanoma/Results/Figures/all.centers.", model, ".", type, ".png"),
        width=1800, height=1800, units="px", res=300)
    out <- PredictionTools::val.surv.mi(p=p, y=S, g=5, time=5,
                                        main="All centers", CI.metrics=TRUE,
                                        lim=c(0,1), dist=TRUE, n.iter=40)
    grDevices::dev.off()

>>>>

    png(file=paste0("Z:/Project Melanoom/PaperMelanoma/Results/Figures/all.centers.", model, ".", type, ".png"),
        width=1800, height=1800, units="px", res=300)
    out <- PredictionTools::val.surv.mi(p=p, y=S, g=5, time=5,
                                        main="All centers", CI.metrics=TRUE,
                                        lim=c(0,1), dist=TRUE)
    grDevices::dev.off()

### 2024-06-20 Code/12_Validation.Rmd
Final edits

```{r, eval=TRUE}
# calibration curve for recurrence
# TODO: validation based on dd.training or dd.validation?
for (data.type in c("training", "validation")){
  for (outcome in c("Rec", "MSM")){
    options(datadist=paste0("dd.", data.type))

@@

    png(file=paste0("Z:/Project Melanoom/PaperMelanoma/Results/Figures/", data.type, ".", outcome, ".All.png"),
        width=1800, height=1800, units="px", res=300)
    par(mar=rep(0, 4))
    PredictionTools::val.surv.mi(p, S,
                                 g=5, main="All patients", time=horizon, 
                                 lim=c(0,1), dist=TRUE, 
                                 CI.metrics=TRUE, n.iter=40,
                                 optimism.C=ifelse(data.type=="training", optimism, 0))
    grDevices::dev.off()

    png(file=paste0("Z:/Project Melanoom/PaperMelanoma/Results/Figures/", data.type, ".", outcome, ".Positive.png"),
        width=1800, height=1800, units="px", res=300)
    par(mar=rep(0, 4))
    PredictionTools::val.surv.mi(p[data$SNstatus=="Positive",],
                                 S[data$SNstatus=="Positive",],
                                 g=5, main="Patients with positive SN", 
                                 time=horizon, lim=c(0,1), dist=TRUE, 
                                 CI.metrics=TRUE, n.iter=40,
                                 optimism.C=ifelse(data.type=="training", optimism, 0))
    grDevices::dev.off()

    png(file=paste0("Z:/Project Melanoom/PaperMelanoma/Results/Figures/", data.type, ".", outcome, ".Negative.png"),
        width=1800, height=1800, units="px", res=300)
    par(mar=rep(0, 4))
    PredictionTools::val.surv.mi(p[data$SNstatus=="Negative",],
                                 S[data$SNstatus=="Negative",],
                                 g=5, main="Patients with negative SN", 
                                 time=horizon, lim=c(0,1), dist=TRUE, 
                                 CI.metrics=TRUE, n.iter=40,
                                 optimism.C=ifelse(data.type=="training", optimism, 0))
    grDevices::dev.off()

>>>>

```{r, eval=TRUE}
# calibration curve for recurrence
# TODO: validation based on dd.training or dd.validation?
for (data.type in c("training", "validation")){
  for (outcome in c("Rec", "MSM")){
    cat("Make calibration plot for", data.type, "data, for the outcome", outcome, "\n")
    options(datadist=paste0("dd.", data.type))

@@

    png(file=paste0("Z:/Project Melanoom/PaperMelanoma/Results/Figures/", data.type, ".", outcome, ".All.png"),
        width=1800, height=1800, units="px", res=300)
    par(mar=rep(0, 4))
    PredictionTools::val.surv.mi(p, S,
                                 g=5, main="All patients", time=horizon, 
                                 lim=c(0,1), dist=TRUE, 
                                 CI.metrics=TRUE,
                                 show.metrics=c(rep(TRUE, 5), FALSE),
                                 optimism.C=ifelse(data.type=="training", optimism, 0))
    grDevices::dev.off()

    png(file=paste0("Z:/Project Melanoom/PaperMelanoma/Results/Figures/", data.type, ".", outcome, ".Positive.png"),
        width=1800, height=1800, units="px", res=300)
    par(mar=rep(0, 4))
    PredictionTools::val.surv.mi(p[data$SNstatus=="Positive",],
                                 S[data$SNstatus=="Positive",],
                                 g=5, main="Patients with positive SN", 
                                 time=horizon, lim=c(0,1), dist=TRUE, 
                                 CI.metrics=TRUE, 
                                 show.metrics=c(rep(TRUE, 5), FALSE),
                                 optimism.C=ifelse(data.type=="training", optimism, 0))
    grDevices::dev.off()

    png(file=paste0("Z:/Project Melanoom/PaperMelanoma/Results/Figures/", data.type, ".", outcome, ".Negative.png"),
        width=1800, height=1800, units="px", res=300)
    par(mar=rep(0, 4))
    PredictionTools::val.surv.mi(p[data$SNstatus=="Negative",],
                                 S[data$SNstatus=="Negative",],
                                 g=5, main="Patients with negative SN", 
                                 time=horizon, lim=c(0,1), dist=TRUE, 
                                 CI.metrics=TRUE, 
                                 show.metrics=c(rep(TRUE, 5), FALSE),
                                 optimism.C=ifelse(data.type=="training", optimism, 0))
    grDevices::dev.off()
